Concurrent Programming in Harmony

### 2021-08-09 book/paper.tex
Renamed Carter to Corey

Unfortunately, the protocol turns out to be incorrect, but it took 17 years before
somebody noticed~\cite{Lowe95}.  Model checking can be used to find the bug~\cite{Lowe96}.
To demonstate the bug, we need a third party, which we will call Carter.
We want to make sure that Carter cannot impersonate Alice or Bob.
However, it is possible that Alice tries to set up an authenticated connection to Carter
using the Needham-Schroeder protocol.  That in itself is not a problem.

The code in \autoref{fig:ns} has Alice try to set up a connection to either Bob
or Carter.  Bob only accepts connections with Alice.  Carter, when receiving a message
that it can decrypt, will try to find an attack by sending every possible message to
every possible destination.  In particular, it keeps track of every nonce that it has
seen and will try to construct messages with them to send to Alice and Bob.
If, at some point, Carter finds the nonce that Bob generates for Alice, then Carter
can impersonate Alice by sending a type~3 message containing that nonce to Bob.

@@

\begin{enumerate}
\item Alice creates a new nonce $N_A$ and sends $\langle 1, A, N_A \rangle_\mathtt{Carter}$
to Carter;
\item Upon receipt, Carter sends $\langle 1, A, N_A \rangle_\mathtt{Bob}$ to Bob;
\item Upon receipt, Bob creates a new nonce $N_B$ and sends
$\langle 2, N_A, N_B \rangle_\mathtt{Alice}$ to Alice;
\item Alice thinks the message came from Carter (because it contains $N_A$, which
Alice sent to Carter) and
sends $\langle 3, N_B \rangle_\mathtt{Carter}$ to Carter.
\item Carter learns $N_B$, which it was not supposed to.
\end{enumerate}

Carter can use $N_B$ to send $\langle 3, N_B \rangle_\mathtt{Bob}$ to Bob.
Bob now thinks it is talking to Alice, even though Alice never tried to
communicate with Bob.

>>>>

Unfortunately, the protocol turns out to be incorrect, but it took 17 years before
somebody noticed~\cite{Lowe95}.  Model checking can be used to find the bug~\cite{Lowe96}.
To demonstate the bug, we need a third party, which we will call Corey.
We want to make sure that Corey cannot impersonate Alice or Bob.
However, it is possible that Alice tries to set up an authenticated connection to Corey
using the Needham-Schroeder protocol.  That in itself is not a problem.

The code in \autoref{fig:ns} has Alice try to set up a connection to either Bob
or Corey.  Bob only accepts connections with Alice.  Corey, when receiving a message
that it can decrypt, will try to find an attack by sending every possible message to
every possible destination.  In particular, it keeps track of every nonce that it has
seen and will try to construct messages with them to send to Alice and Bob.
If, at some point, Corey finds the nonce that Bob generates for Alice, then Corey
can impersonate Alice by sending a type~3 message containing that nonce to Bob.

@@

\begin{enumerate}
\item Alice creates a new nonce $N_A$ and sends $\langle 1, A, N_A \rangle_\mathtt{Corey}$
to Corey;
\item Upon receipt, Corey sends $\langle 1, A, N_A \rangle_\mathtt{Bob}$ to Bob;
\item Upon receipt, Bob creates a new nonce $N_B$ and sends
$\langle 2, N_A, N_B \rangle_\mathtt{Alice}$ to Alice;
\item Alice thinks the message came from Corey (because it contains $N_A$, which
Alice sent to Corey) and
sends $\langle 3, N_B \rangle_\mathtt{Corey}$ to Corey.
\item Corey learns $N_B$, which it was not supposed to.
\end{enumerate}

Corey can use $N_B$ to send $\langle 3, N_B \rangle_\mathtt{Bob}$ to Bob.
Bob now thinks it is talking to Alice, even though Alice never tried to
communicate with Bob.
